Best Practices for Alchemical Free Energy Calculations: v\versionnumber

### 2019-12-11 paper/manuscript.tex
adding sampling scheme section

\subsubsection*{What different samples schemes exist and which one should I use?}

\begin{figure}
    \includegraphics[width=0.95\columnwidth]{paper/figures/fig7_sampl_scheme/sampling_schemes.pdf}
    \caption{\textbf{There are 4 different sampling strategies available and implemntations are availble for different software packages.} A: Multiple replicas in parallel at different lambda states. B: Hamiltonian replica exchange scheme. C: Single replica scheme sampling from all $\lambda$ states. D: Non-equilibrium sampling scheme.}
    \label{fig:fig7_sampling_scheme}
\end{figure}

@@

MBAR is provably the lowest variance asymptotically unbiases estimator of the free energies given the energies of the samples~\cite{zqtan}. It also provides an uncertainty estimate, which has been shown to be accurate as long as there are sufficient samples at each state~\cite{paliwal2011benchmark}.

>>>>

\subsubsection*{What different sampling schemes exist and which one should I use?}

\ref{fig:fig7_ampling_scheme} A:\cite{hedges2019biosimspace, song2019using } B\cite{aldeghi2015accurate, wang2015accurate,jiang2019computing} C:\cite{li2007simulated, tan2017optimally} D:\cite{aldeghi2018accurate}
\begin{figure}
    \includegraphics[width=0.95\columnwidth]{paper/figures/fig7_sampl_scheme/sampling_schemes.pdf}
    \caption{\textbf{There are 4 different sampling strategies available and implementations are available for different software packages.} A: Multiple replicas in parallel at different lambda states. B: Hamiltonian replica exchange scheme. C: Single replica scheme sampling from all $\lambda$ states. D: Non-equilibrium sampling scheme.}
    \label{fig:fig7_sampling_scheme}
\end{figure}

@@

MBAR is provably the lowest variance asymptotically unbiased estimator of the free energies given the energies of the samples~\cite{tan2004likelihood}. It also provides an uncertainty estimate, which has been shown to be accurate as long as there are sufficient samples at each state~\cite{paliwal2011benchmark}.
